An asymptotically normal out-of-sample test based on mixed estimation windows

### 2017-05-19 S2-normality.tex
Move Theorem and Lemma source code to main LaTeX files

\phantomsection
\addcontentsline{toc}{subsubsection}{Theorem \ref{res:1}}
\begin{thm}\label{res:1}\input{mixedwindow_thm1}\end{thm}

@@

\phantomsection
\addcontentsline{toc}{subsubsection}{Lemma \ref{lem:2}}
\begin{lem}\label{lem:2}\input{mixedwindow_lem2}\end{lem}

@@

\phantomsection
\addcontentsline{toc}{subsubsection}{Theorem \ref{thm:3}}
\begin{thm}\label{thm:3}\input{mixedwindow_thm3}\end{thm}

>>>>

\phantomsection
\addcontentsline{toc}{subsubsection}{Theorem \ref{res:1}}
\begin{thm}\label{res:1}
  If Assumptions~\ref{a1}--\ref{a4} hold then
  \begin{equation*}
    \sqrt{P} (\fb - \E \fb^*) \to^d N(0, \sigma^2),
  \end{equation*}
  with $\sigma^2 = s_1 + 2(s_2 + s_3)$ and
  \begin{align*}
    s_1  &= \lim \var(\sqrt{P}\, \fb^*), &
    s_2  &= \lim \cov(\sqrt{P}\, \fb^*, \sqrt{P}\, \gb^*), &
    s_3  &= \lim \var(\sqrt{P}\, \gb^*).
  \end{align*}
\end{thm}

@@

\phantomsection
\addcontentsline{toc}{subsubsection}{Lemma \ref{lem:2}}
\begin{lem}\label{lem:2}
  If Assumptions~\ref{a1}--\ref{a5} hold then
  \begin{equation*}
    \sigmah_1^2 \to^p \sigma^2.
  \end{equation*}
  If Assumptions~\ref{a1}--\ref{a4} hold and $\{\varepsilon_{t},
  \Fs_t\}$ is an \mds\ then
  \begin{equation*}
    \sigmah_2^2 \to^p \sigma^2.
  \end{equation*}
\end{lem}

@@

\phantomsection
\addcontentsline{toc}{subsubsection}{Theorem \ref{thm:3}}
\begin{thm}\label{thm:3}
  If Assumptions~\ref{a1}--\ref{a5} hold, then
  \begin{equation*}
    \sqrt{P} \fb / \sigmah_1 \to^d N(0, 1)
  \end{equation*}
  under the null hypothesis $\E(\varepsilon_{t+1} \yh_{t+1}) = 0$ for
  all $t = R,\dots,T-1$.  If, instead, Assumptions~\ref{a1}--\ref{a4}
  hold, then
  \begin{equation*}
    \sqrt{P} \fb / \sigmah_2 \to^d N(0, 1)
  \end{equation*}
  under the null hypothesis that $\{\varepsilon_t, \Fs_t\}$ is an \mds.
\end{thm}
